### 2012-05-03 2.2.1.tex
another day at the office

%\subsubsection{Prediction distributions}

\citet{Coltheart1977}

\citet{Hayes2008a}
\citet{Albright2009a}

>>>>

\subsubsection{Prediction distributions}

\begin{table}
\centering

\begin{tabular}{l l l l l}
\toprule
Spearman $\rho$             & MaxEnt         & density        & bigram         & attested onsets/rimes \\
\midrule
\citeauthor{Greenberg1964a} & 0.765          & 0.648          & 0.863          & \textbf{0.845}        \\
\citeauthor{Scholes1966}    & 0.762          & 0.718          & \textbf{0.827} & 0.791                 \\
\citeauthor{Albright2003a}  & 0.429          & \textbf{0.742} & 0.708          & 0.725                 \\
\citeauthor{Albright2007}   & \textbf{0.926} & 0.619          & 0.523          & 0.793                 \\
\bottomrule
Kendall $\tau_b$            & MaxEnt         & density & bigram & attested onsets/rimes \
\midrule
\citeauthor{Greenberg1964a} & 0.585          & 0.462   & 0.692  & \textbf{0.716}      \\
\citeauthor{Scholes1966}    & 0.597          & 0.565   & 0.652  & \textbf{0.664}      \\
\citeauthor{Albright2003a}  & 0.343          & 0.556   & 0.506  & \textbf{0.599}      \\
\citeauthor{Albright2007}   & \textbf{0.788} & 0.462   & 0.371  & 0.659               \\
\bottomrule
Goodman-Kruskal $\gamma$    & MaxEnt & density & bigram & attested onsets/rimes
\midrule
\citeauthor{Greenberg1964a} & 0.684  & 0.462   & 0.692  & \textbf{1.000} \\
\citeauthor{Scholes1966}    & 0.634  & 0.614   & 0.667  & \textbf{0.995} \\
\citeauthor{Albright2003a}  & 0.656  & 0.575   & 0.509  & \textbf{0.953} \\
\citeauthor{Albright2007}   & 0.871  & 0.498   & 0.373  & \textbf{0.977} \\
\bottomrule
\end{tabular}

\caption{Here is my caption.  All values are significant at $\alpha = 0.05$}
\end{table}

\begin{table}
\centering

\begin{tabular}{l r r r}
\toprule
Spearman $\rho$             & MaxEnt              & density             & bigram              \\
\midrule
\citeauthor{Greenberg1964a} & 0.185               & 0.154               & \textbf{0.319}      \\
\citeauthor{Scholes1966}    & 0.122               & 0.174               & \ul{\textbf{0.292}} \\
\citeauthor{Albright2003a}  & 0.011               & \ul{\textbf{0.246}} & 0.203               \\
\citeauthor{Albright2007}   & \ul{\textbf{0.440}} & \ul{0.340}          & 0.016               \\ 
\bottomrule
Kendall $\tau_b$            & MaxEnt              & density             & bigram \\
\midrule
\citeauthor{Greenberg1964a} & 0.135               & 0.077               & \textbf{0.205}      \\
\citeauthor{Scholes1966}    & 0.098               & 0.124               & \ul{\textbf{0.206}} \\
\citeauthor{Albright2003a}  & 0.005               & \ul{\textbf{0.157}} & 0.126               \\
\citeauthor{Albright2007}   & \ul{\textbf{0.340}} & 0.215               & $-$0.017            \\
\bottomrule
Goodman-Kruskal $\gamma$    & MaxEnt              & density             & bigram \\
\midrule
\citeauthor{Greenberg1964a} & \ul{0.158}          & 0.077               & \ul{\textbf{0.205}} \\
\citeauthor{Scholes1966}    & 0.105               & 0.137               & \ul{\textbf{0.214}} \\
\citeauthor{Albright2003a}  & 0.010               & \ul{\textbf{0.162}} & \ul{0.127}          \\
\citeauthor{Albright2007}   & \ul{\textbf{0.376}} & 0.232               & 0.017               \\
\bottomrule
\end{tabular}

\caption{Here is my caption; underlined values are significant at $\alpha = 0.05$}
\end{table}

%\citet{Coltheart1977}
%
%\citet{Hayes2008a}
%\citet{Albright2009a}

### 2012-05-03 3.1.1.tex
another day at the office

There are however a few complications. First, not all polysyllabic roots conform to \textsc{Backness Harmony}. In this case, as can be seen from (\ref{turkexcept}a), suffix vowels generally harmonize with the final root vowel. 
There is also a small class of nouns, shown in (\ref{turkexcept}b), which exhibit [$-$\textsc{Back}] suffix vowels despite the fact that their final root vowel is [$+$\textsc{Back}].

@@

It is uncontroversial that the disharmonic suffixes of (\ref{turkexcept}b) are no more than very sporadic exceptions to \textsc{Backness Harmony}, root disharmony has ben the subject of much debate.  As disharmonic roots still trigger suffix harmony, \citet[][212, 289]{Anderson1974} proposes to distinguish suffix harmony (an alternation) from a sequence structure constraint governing root harmony.

However, as \citet[][?]{Zonneveld1978} notes, the theory of exceptionality proposed in \emph{SPE} (p.~374f.) provides a direct account of suffix harmony in disharmonic roots. \citeauthor{SPE} assume that the specification of the target (i.e., the segment or segments to be changed) of a rule $R$ must be marked [$+$rule $R$] by convention. A root or affix which fails to undergo $R$ despite otherwise matching the structural description is simply said to be marked [$-$rule $R$]. Under this account, exceptionality boils down to failing to match an extended structural description. If disharmonic roots are marked [$-$\textsc{Backness Harmony}], then the final vowel of disharmonic roots will still trigger \textsc{Backness Harmony}, since the [$-$\textsc{Backness Harmony}] root is no longer the target but rather the environment, which is not subject to the [$+$\textsc{Backness Harmony}] requirement.

>>>>

There are a few complications, however. First, not all polysyllabic roots conform to \textsc{Backness Harmony}. In this case, as can be seen from (\ref{turkexcept}a), suffix vowels generally harmonize with the final root vowel. There is also a small class of nouns, shown in (\ref{turkexcept}b), which exhibit [$-$\textsc{Back}] suffix vowels despite the fact that their final root vowel is [$+$\textsc{Back}].

@@

It is uncontroversial that the disharmonic suffixes of (\ref{turkexcept}b) are no more than very sporadic exceptions to \textsc{Backness Harmony}, root disharmony has ben the subject of much debate. As disharmonic roots still trigger suffix harmony, \citet[][212, 289]{Anderson1974} proposes to distinguish suffix harmony (an alternation) from a sequence structure constraint governing root harmony. This point is echoed by \citet{Iverson1978}.

However, as \citet[][197f.]{Zonneveld1978} notes, the theory of exceptionality proposed in \emph{SPE} (p.~374f.) provides a direct account of suffix harmony in disharmonic roots. \citeauthor{SPE} assume that the specification of the target (i.e., the segment or segments to be changed) of a rule $R$ must be marked [$+$rule $R$] by convention. A root or affix which fails to undergo $R$ despite otherwise matching the structural description is simply said to be marked [$-$rule $R$]. Under this account, exceptionality boils down to failing to match an extended structural description. If disharmonic roots are marked [$-$\textsc{Backness Harmony}], then the final vowel of disharmonic roots will still trigger \textsc{Backness Harmony}, since the [$-$\textsc{Backness Harmony}] root is no longer the target but rather the environment, which is not subject to the [$+$\textsc{Backness Harmony}] requirement.
